Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Reviewing Methodology pt. I, with some comments also

First, after the publishing company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
Then, a Feature Selection (FS) process \cite{kittler1986feature} has
been carried out, as it is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}. The aim of these
% Did you know there were noisy features? Why? 
% You should include in the previous section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ 
algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem. 
  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
methods.  
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

>>>>

First, after the publishing company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. % (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
Furthermore, the initial set of variables, presented
in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}. % (Paloma) Where are they? In table 2?

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
Then, a Feature Selection (FS) process \cite{kittler1986feature} has
been carried out, as it is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}. The aim of these
% Did you know there were noisy features? Why? 
% You should include in the previous section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ 
algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem. 
  In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.
